Keyword Categorization and Emotion Analysis in Voice Calls

### 2020-12-03 msccls/MScTemplateCS.tex
Updates from Overleaf

\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}
\usepackage{natbib}
\usepackage{wrapfig}

@@

\chapter{Theory}
\section{Machine Learning}
Machine learning is a field of study in artificial intelligence that aims to train a system to solve a problem, rather than to explicitly program it. By being presented with large amounts of data associated with the task at hand, the system algorithmically builds a statistical model that discovers structures in the data and allows the system to identify rules for the problem. 
In \textbf{supervised learning}, which is one of the two main types of tasks in machine learning, the dataset is the collection of labeled examples $\{(\mathbf{x}_i, y_i)\}_{i=1}^N.$ Each element $\mathbf{x}_i$ is a feature vector that contains a value describing the example somehow and $y_i$ is a label, which is either a finite set of classes or a real number. The purpose of supervised learning is to use the dataset to produce a model that takes a feature vector x as input and outputs information that allows deducing the label y for this feature vector.) 
The other main type of tasks in machine learning is \textbf{unsupervised learning}. The dataset for unsupervised learning is $\{ (\mathbf{x}_i)\}_{i=1}^N$ where $\mathbf{x}_i$ is a feature vector. The goal of unsupervised learning is to use the dataset to produce a model that takes a feature vector x as input and outputs either another vector or a value.

(Källor Andriy Burkov, Chollet)

@@

Neural networks are machine learning systems loosely inspired by biological neural networks (Chollet s.8). A neural network is a collection of connected nodes or neurons that

\begin{quote}
An ANN is based on a collection of connected units or nodes called artificial neurons, which loosely model the neurons in a biological brain. Each connection, like the synapses in a biological brain, can transmit a signal to other neurons. An artificial neuron that receives a signal then processes it and can signal neurons connected to it.
\end{quote}

Deep learning = multiple layers of neural networks

@@

\subsection{Word Embedding}
To resolve the two aforementioned problems with one-hot encodings, word embeddings were created, also known as dense word vectors. \citep{neuralnetworkmethods} 
Here, instead of creating a sparse, hardcoded vector with equal distance between words, they are learned from data and packed into a lower-dimensional vector where each dimension contains some relevant data about the word. According to \citet{franoischollet2017learning}, word embeddings that are 256-dimensional, 512-dimensional or 1024-dimensional are common when dealing with very large vocabularies, in contrast to the 20 000-dimensional one that would be created if one were to use one-hot encoding. Additionally, the geometric relationship between words can and should reflect the semantic relationship between those same words. This means that synonyms and words often used together are embedded closer to each other, while words seldom used together are more distant in the embedding. In addition to distance, direction could also be a useful tool to extract meaning from the embedding.\newpage

\begin{wrapfigure}{r}{0.25\textwidth}
\includegraphics[width=0.9\linewidth]{msccls/embedding_direction.png} 
\caption{Small example of a word embedding space}
\label{fig:direction}
\end{wrapfigure}

@@

\section{Evaluation}
\subsection{F1-score, precision, accuracy}
\chapter{Approach}

@@

\section{Theory}
NLP technique, categorization, ML, supervised/unsupervised,  
Mechanical turks to 
Finns både text och audio på MELD, \citep{zhang2019modeling} visar att text för sig är bättre än ljud men att text+ljud > text
train, dev(validation), test, man testar på dev under development, först på test efter man är klar
\section{Datasets}
\subsection{Approach} 
\section{Method}
Google Colab
Word level one hot encoding, kanske relevant, avgör beroende på hur mycket mer vi behöver skriva.
\section{Implementation}
Overfitting \\
Data Augmentation \\
importance of finding the correct data-sets \\
\section{Bibtesting, will be removed}
\citep{emotionlinesdataset} \\
\citep{franoischollet2017learning}\\
\citep{beaver2020towards}
\chapter{Speech-to-text}
Vi antar att det är 2 speakers i samtalet, nämn för- och nackdelar. Ta med i limitations
Vi har endast stöd för engelska pga limits i datamängd, dokumentation. 
Google diarization är i Beta.
Använda kategoriserade ord i Googles STTs speechContexts och därefter använda ML igen för att få högre precision på kategorisering. 
Sample rates 8000 vs 48000 t.ex.

@@

\section{Results}
\section{Discussion}

>>>>

\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}
\usepackage{natbib}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{amsmath}

@@

\chapter{Theory}
\section{Machine Learning}
Machine learning \citep{franoischollet2017learning} is a field of study in artificial intelligence that aims to train a system to solve a problem, rather than to explicitly program it. By being presented with large amounts of data associated with the task at hand, the system algorithmically builds a statistical model that discovers structures in the data and allows the system to identify rules for the problem. 
In \textbf{supervised learning} \citep{100pageBurkov}, which is one of the two main types of tasks in machine learning, the dataset is the collection of labeled examples $\{(\mathbf{x}_i, y_i)\}_{i=1}^N.$ Each element $\mathbf{x}_i$ is a feature vector that contains a value describing the example somehow and $y_i$ is a label, which is either a finite set of classes or a real number. The purpose of supervised learning is to use the dataset to produce a model that takes a feature vector x as input and outputs information that allows deducing the label y for this feature vector.) 
The other main type of tasks in machine learning is \textbf{unsupervised learning}. The dataset for unsupervised learning is $\{ (\mathbf{x}_i)\}_{i=1}^N$ where $\mathbf{x}_i$ is a feature vector. The goal of unsupervised learning is to use the dataset to produce a model that takes a feature vector x as input and outputs either another vector or a value.

@@

Neural networks are machine learning systems loosely inspired by biological neural networks. A neural network is a collection of connected nodes or neurons that was first mentioned in \citet{mcculloch1943}. A neuron \citep{dawson1998ann} is an information-processing unit that receives inputs and produces a single output that can be sent to multiple other neurons. To find the output of a neuron the weighted sum of all inputs is weighted by the weights all connecting to the neuron. This weighted sum is then passed through an activation function to provide the output.

\begin{quote}
RNN gate    
\end{quote}

\begin{quote}
    The learning of the error is the cost function of the network and feeding back is called backpropagation.

\end{quote}

\begin{figure}[htp]
    \centering
    \includegraphics[width=12cm]{msccls/explanatory_images/single_neuron.png}
    \caption{An example of a single neuron}
    \label{fig:neuron}
\end{figure}

\begin{equation}
    g(x_1, x_2, x_3,...,x_n) = g(x) = \sum_{i=1}^n  xi
\end{equation}

Here, $g(x)$ takes the inputs $x_1, x_2, x_3,...,x_n$, while the activation function $f(x)$ defines the output. An example of a well known activation function is ReLU, Rectified linear unit, which has the following function.

\begin{equation}
y = f(g(x)) =
\begin{cases}
  0, & \text{if}\ x \leq 0 \\
  x, & \text{if}\ x > 0
\end{cases}
\end{equation}

\begin{itemize}
    \item Neurons
    \item Weights and connections 
    \item Backpropagation function
    \item gradient
    \item Deep learning = multiple layers of neural networks
\end{itemize}

\subsection{Gated Recurrent Unit - GRU}
A gated recurrent unit (GRU) is neural network architecture introduced in 2014 by \citet{cho2014learning} and is considered an improvement to the traditional recurrent neural network. Although fairly new it is already a well-established variant of recurrent neural networks. A GRU is quite useful for solving the vanishing gradient problem \citep{hochreiter1998} that might occur in recurrent neural networks. The vanishing gradient problem occurs in machine learning when the gradient progressively decreases, which prevents the adjustments of the weight's values. It has also been shown that GRUs have had better performance on smaller and less frequent datasets \citep{Gruber2020AreGC}.
GRUs is primarily constructed of an update gate, a reset gate and a current memory gate. The update gate regulates the amount of information that is passed along to the next state, while the reset gate on the other hand decides the amount of past information that is going to being disregarded henceforth.

\begin{quote}
Snacka mer om current memory gate eller ta bort helt
\end{quote}

\subsection{Long Short-Term Memory - LSTM}

\begin{quote}
    Ta bara med ifall vi bestämmer oss att ändra från GRU till LSTM i modellen
    In comparison to GRUs, LSTMs are

\end{quote}

@@

\subsection{Word Embedding}
To resolve the two aforementioned problems with one-hot encodings, word embeddings were created, also known as dense word vectors. \citep{neuralnetworkmethods} 
Here, instead of creating a sparse, hardcoded vector with equal distance between words, they are learned from data and packed into a lower-dimensional vector where each dimension contains some relevant data about the word. According to \citet{franoischollet2017learning}, word embeddings that are 256-dimensional, 512-dimensional or 1024-dimensional are common when dealing with very large vocabularies, in contrast to the 20 000-dimensional one that would be created if one were to use one-hot encoding. Additionally, the geometric relationship between words can and should reflect the semantic relationship between those same words. This means that synonyms and words often used together are embedded closer to each other, while words seldom used together are more distant in the embedding. In addition to distance, direction could also be a useful tool to extract meaning from the embedding.\newpage %Temp for formatting, don't forget it's here

\begin{wrapfigure}{r}{0.25\textwidth}
\includegraphics[width=0.9\linewidth]{msccls/explanatory_images/embedding_direction.png} 
\caption{Small example of a word embedding space}
\label{fig:direction}
\end{wrapfigure}

@@

\section{Evaluation}
\subsection{F1-score, precision, accuracy}

@@

\section{Theory}
NLP technique, categorization, ML, supervised/unsupervised,  
Mechanical turks to 
Finns både text och audio på MELD, \citep{zhang2019modeling} visar att text för sig är bättre än ljud men att text+ljud > text
train, dev(validation), test, man testar på dev under development, först på test efter man är klar

\chapter{Implementation}

\section{Datasets}

\subsection{Approach} 
\section{Method}
Google Colab
Word level one hot encoding, kanske relevant, avgör beroende på hur mycket mer vi behöver skriva.
\section{Implementation}
Overfitting \\
Data Augmentation \\
importance of finding the correct data-sets \\
\section{Bibtesting, will be removed}
\citep{emotionlinesdataset} \\
\citep{franoischollet2017learning}\\
\citep{beaver2020towards}
\chapter{Speech-to-text}
Vi antar att det är 2 speakers i samtalet, nämn för- och nackdelar. Ta med i limitations
Vi har endast stöd för engelska pga limits i datamängd, dokumentation. 
Google diarization är i Beta.
Använda kategoriserade ord i Googles STTs speechContexts och därefter använda ML igen för att få högre precision på kategorisering. 
Sample rates 8000 vs 48000 t.ex.

@@

\section{Results}

These are our results

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{center}
\begin{tabular}{|c|cc|cc|cc|cc|}
\hline
\multirow{2}{*}{Methods} & \multicolumn{2}{c|}{MELD 34}            & \multicolumn{2}{c|}{DailyDialog 45}     & \multicolumn{2}{c|}{IEMOCAP 34}         & \multicolumn{2}{c|}{EmoryNLP 23}        \\ \cline{2-9} 
                         & \multicolumn{1}{c|}{W-Avg F1} & Loss & \multicolumn{1}{c|}{W-Avg F1} & Loss & \multicolumn{1}{c|}{W-Avg F1} & Loss & \multicolumn{1}{c|}{W-Avg F1} & Loss \\ \hline
Cosmic                   & 64.14                         & 2.68 & 60.01                         & 2.94 & 58.77                         & 0.96 & 42.55                         & 2.48 \\ \hline
Vår modell               &                               &      &                               &      &                               &      &                               &      \\ \hline
\end{tabular}
\end{center}

\section{Discussion}
This is the discussion about our results
